In this report we focus on groups which arise from the solution set of polynomial equations over finite fields. The most famous of these groups is the set of points on an elliptic curve characterized by the equation $y^2 = x^3 + ax + b$ where $a,b \in \mathbb{F}_p$ satisfy $4a^3 + 27b^2 \not\equiv 0 \text{ mod } p$. In recent years, groups arising from these equation have found significant success in public key cryptography even though it is still an open questions whether these kind of groups are actually cryptographically secure! One of the benefits of elliptic curves is that the fastest known attack on them has $O(\sqrt{N})$ complexity, where $N$ is the order of the group. This means significantly smaller keys can be used in comparison to the key length of RSA. A natural question is 

$$
\textbf{What about other polynomial equations?}
$$ 

It turns out that there are infinitely many groups which arise from the solution sets of polynomial equations. Which of these groups are cryptographically viable is a vast active area of research. First we develop some notations required to describe these groups. \\ 

Let $K$ be a field. Let $A = K[x_1,...,x_n]$ represent the polynomial ring in $n$ variables over $K$. Given a subset $T \subseteq A$, we may define 
$$
Z(T) = \lbrace P \in K^n \mid f(P) = 0 \text{ for all } f \in T \rbrace 
$$
to be the set of all common zeros of polynomials in $T$. We call $Y \subseteq K^n $ an \textit{algebraic set} if $Y = Z(T)$ for some subset $T \subseteq A$. A not so obvious but usual fact to keep in mind is that if $T \subseteq A$ and $J = \langle T \rangle $ is the ideal generated by elements of $T$, then $Z(T) = Z(J)$. We say an algebraic set $Y$ is reducible if it can be written as the union of two smaller algebraic sets. For example, let $Y = Z(x^2 - yz, xz-x)$ as a subset of $\mathbb{C}^3$. That is, $Y$ is the set of complex valued points in $\mathbb{C}^3$ which satisfy each of the equations $x^2 - yz$ and $xz-x$. Notice that
\begin{align*}
	Y &= Z(x^2 - yz, xz-x) \\
	&= Z(x^2 - yz, x(z-1)) \\
	&= Z(x^2 - yz,x) \cup Z(x^2 - yz,z-1) \\
	&= Z(yz,x) \cup Z(x^2 - yz,z -1) \\
	&= Z(y,x) \cup Z(z,x) \cup Z(x^2 - yz, z - 1)
\end{align*} 
So $Y$ is reducible in $\mathbb{C}^3$. If an algebraic set is not reducible, it is called irreducible. It is the irreducible algebraic set which we shall loosely call \textit{algebraic varieties}. For example, take the curve $y^2 = x^3 + ax + b \in \mathbb{F}_p[x,y]$ where $4a^3 + 27b^2 \not\equiv 0 \text{ mod } p$. Then $E = Z(y^2 = x^3 + ax + b)$ is an algebraic variety. In fact, it is the simplest example of an \textit{abeilan variety} - A projective complete algebraic variety with a group structure on its points given by smooth morphisms. This definition is beyond what is important for this report, but essentially, an abelian variety is a set of solutions of polynomials which can be endowed with operations on its points which make it into a group. These are precisely the groups which arise from polynomial eqautions. For the remaining sections of this report, we will discuss abelian varieties of dimension $1$. That is plane curves over finite fields.  


